---
title: "P8106_HW3_SY3352"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo = T, message = FALSE, results='hide'}
library(caret)
library(glmnet)
library(tidymodels)
library(pROC)
library(earth)
library(pdp)
library(MASS)
```

```{r}
dat <- read.csv("auto.csv") |> na.omit()

dat$origin <- as.factor(dat$origin)
dat$mpg_cat <- as.factor(dat$mpg_cat)
contrasts(dat$mpg_cat)

set.seed(1514)
data_split <- initial_split(dat, prop = 0.70)
training_data <- training(data_split)
testing_data  <- testing(data_split)
```

# Problem (a)
```{r}
glm.fit <- glm(mpg_cat ~ .,
               data = training_data,
               family = binomial(link = "logit"))
summary(glm.fit)
```
From the model result, I would say that there are redundant predictors in the model as some predictors has a p value > 0.05, meaning that they are not significant in predicting the response. These predictors are: `cylinders`, `displacement`, `horsepower`, `acceleration`, and `origin3` (Japanese).

# Problem (b)
```{r}
ctrl <- trainControl(method = "cv", number = 10,
                     summaryFunction = twoClassSummary,
                     classProbs = TRUE)
set.seed(1514)
model.mars <- train(x = training_data[1:7], y = training_data$mpg_cat,
                    method = "earth",
                    tuneGrid = expand.grid(degree = 1:4, 
                                           nprune = 2:20),
                    metric = "ROC",
                    trControl = ctrl)
model.mars$bestTune
plot(model.mars)

set.seed(1514)
model.cv.glm <- train(x = training_data[1:7], y = training_data$mpg_cat,
                   method = "glm",
                   metric = "ROC",
                   trControl = ctrl)

res <- resamples(list(GLM = model.cv.glm, MARS = model.mars))
summary(res)
bwplot(res, metric = "ROC")
```
From the resample result, MARS has higher median in ROC and Specificity, lower in Sensitivity compared with logistic regression, though the differences are very small. I would say that here MARS does improve the prediction performance, but the improvement is slight.

# Problem (c) 
```{r}
lda.fit <- lda(mpg_cat~., data = training_data)
plot(lda.fit)
A <- lda.fit$scaling
A
```

# Problem (d)
```{r}
set.seed(1514)
model.cv.lda <- train(mpg_cat~., data = training_data,
                   method = "lda",
                   metric = "ROC",
                   trControl = ctrl)

res_d <- resamples(list(GLM = model.cv.glm, 
                        MARS = model.mars, 
                        LDA = model.cv.lda))
summary(res_d)
bwplot(res_d, metric = "ROC")
```
From the resample result, LDA has the lowest median in ROC and Specificity in the three models except for Sensitivity. It can be concluded that LDA here performs worse than previously used MARS and GLM. Thus here I stick with the choice made in (b) that MARS is the best model. I choose MARS to predic the response.

```{r}
mars.pred <- predict(model.mars, newdata = testing_data, type = "prob")[, 2]
roc.mars <- roc(testing_data$mpg_cat, mars.pred)
plot(roc.mars, legacy.axes = TRUE)
plot(smooth(roc.mars), col = 4, add = TRUE)

roc.mars$auc[1]
```
The AUC for MARS is `r roc.mars$auc[1]`.

# Problem (e)
I decide to choose a probability threshold of 0.5. In a context like this (car fuel efficiency), there is no strong need to consider for cost of false negative like in detecting cancer. For a non-medical context a default 0.5 should be reasonable, as it treats both classes equally and predicts the most probable class for each observation.
```{r}
test.pred <- rep("high", length(mars.pred))
test.pred[mars.pred > 0.5] <- "low"

confusionMatrix(data = as.factor(test.pred),
                reference = testing_data$mpg_cat,
                positive = "low")
```
Under a 0.5 threshold, the confusion matrix gave **Accuracy : 0.9153 (with CI 0.8497, 0.9586)**, which means that true negative+true  positive takes 91.53% of the data, which indicates that this model is quite good. **No Information Rate : 0.5085** gives the majority class, which takes 50.85%. This is very balanced, indicating that the classifier is very good combined with a high accuracy. The very small P-Value further proves that. **Kappa : 0.83** means that the agreement between my classifier and the true label is quite high. **Sensitivity : 0.8276** and **Specificity : 1.0000** are both very high. As sensitivity is a little bit lower, it indicates that the model is more likely to predict low-mpg cars as high. However this is just some minor issues, overall the model works very well from the confusion matrix results.
