---
title: "P8106_HW3_SY3352"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo = T, message = FALSE, results='hide'}
library(caret)
library(glmnet)
library(tidymodels)
library(pROC)
library(earth)
library(pdp)
library(MASS)
```

```{r}
dat <- read.csv("auto.csv") |> na.omit()

dat$origin <- as.factor(dat$origin)
dat$mpg_cat <- as.factor(dat$mpg_cat)

set.seed(1514)
data_split <- initial_split(dat, prop = 0.70)
training_data <- training(data_split)
testing_data  <- testing(data_split)
```

# Problem (a)
```{r}
glm.fit <- glm(mpg_cat ~ .,
               data = training_data,
               family = binomial(link = "logit"))
summary(glm.fit)
```
From the model result, I would say that there are redundant predictors in the model as some predictors has a p value > 0.05, meaning that they are not significant in predicting the response. These predictors are: `cylinders`, `displacement`, `horsepower`, `acceleration`, and `origin3` (Japanese).

# Problem (b)
```{r}
ctrl <- trainControl(method = "cv", number = 10,
                     summaryFunction = twoClassSummary,
                     classProbs = TRUE)
set.seed(1514)
model.mars <- train(x = training_data[1:7], y = training_data$mpg_cat,
                    method = "earth",
                    tuneGrid = expand.grid(degree = 1:4, 
                                           nprune = 2:20),
                    metric = "ROC",
                    trControl = ctrl)
model.mars$bestTune
plot(model.mars)

set.seed(1514)
model.cv.glm <- train(x = training_data[1:7], y = training_data$mpg_cat,
                   method = "glm",
                   metric = "ROC",
                   trControl = ctrl)

res <- resamples(list(GLM = model.cv.glm, MARS = model.mars))
summary(res)
bwplot(res, metric = "ROC")
```
From the resample result, MARS has higher median in ROC and Specificity, lower in Sensitivity compared with logistic regression, though the differences are very small. I would say that here MARS does improve the prediction performance, but the improvement is slight.

# Problem (c) 
```{r}

```

# Problem (d)

# Problem (e)
