---
title: "P8106_HW3_SY3352"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, echo = T, message = FALSE, results='hide'}
library(caret)
library(glmnet)
library(tidymodels)
library(pROC)
library(earth)
library(pdp)
library(MASS)
```

```{r}
dat <- read.csv("auto.csv") |> na.omit()

dat$origin <- as.factor(dat$origin)
dat$mpg_cat <- as.factor(dat$mpg_cat)

set.seed(1514)
data_split <- initial_split(dat, prop = 0.70)
training_data <- training(data_split)
testing_data  <- testing(data_split)
```

# Problem (a)
```{r}
glm.fit <- glm(mpg_cat ~ .,
               data = training_data,
               family = binomial(link = "logit"))
summary(glm.fit)
```
From the model result, I would say that there are redundant predictors in the model as some predictors has a p value > 0.05, meaning that they are not significant in predicting the response. These predictors are: `cylinders`, `displacement`, `horsepower`, `acceleration`, and `origin3` (Japanese).

# Problem (b)
```{r}
ctrl <- trainControl(method = "cv", number = 10,
                     summaryFunction = twoClassSummary,
                     classProbs = TRUE)
set.seed(1514)
model.mars <- train(x = training_data[1:7], y = training_data$mpg_cat,
                    method = "earth",
                    tuneGrid = expand.grid(degree = 1:4, 
                                           nprune = 2:20),
                    metric = "ROC",
                    trControl = ctrl)
model.mars$bestTune
plot(model.mars)

set.seed(1514)
model.cv.glm <- train(x = training_data[1:7], y = training_data$mpg_cat,
                   method = "glm",
                   metric = "ROC",
                   trControl = ctrl)

res <- resamples(list(GLM = model.cv.glm, MARS = model.mars))
summary(res)
bwplot(res, metric = "ROC")
```
From the resample result, MARS has higher median in ROC and Specificity, lower in Sensitivity compared with logistic regression, though the differences are very small. I would say that here MARS does improve the prediction performance, but the improvement is slight.

# Problem (c) 
```{r}
lda.fit <- lda(mpg_cat~., data = training_data)
plot(lda.fit)
A <- lda.fit$scaling
A
```

# Problem (d)
```{r}
set.seed(1514)
model.cv.lda <- train(mpg_cat~., data = training_data,
                   method = "lda",
                   metric = "ROC",
                   trControl = ctrl)

res_d <- resamples(list(GLM = model.cv.glm, 
                        MARS = model.mars, 
                        LDA = model.cv.lda))
summary(res_d)
bwplot(res_d, metric = "ROC")
```
From the resample result, LDA has the lowest median in ROC and Specificity in the three models except for Sensitivity. It can be concluded that LDA here performs worse than previously used MARS and GLM. Thus here I stick with the choice made in (b) that MARS is the best model. I choose MARS to predic the response.

```{r}
mars.pred <- predict(model.mars, newdata = testing_data, type = "prob")[, 2]
roc.mars <- roc(testing_data$mpg_cat, mars.pred)
plot(roc.mars, legacy.axes = TRUE)
plot(smooth(roc.mars), col = 4, add = TRUE)

roc.mars$auc[1]
```
The AUC for MARS is `r roc.mars$auc[1]`.

# Problem (e)
```{r}

```

